---
title: "Social Capital"
author: "David Kane"
date: "2022-08-02"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(stringr)
```



```{r, echo = FALSE, message = FALSE}
ec <- read_rds("ec.rds")
#Bristol bay, alaska, 
#Denali, Alaska
#Lake and Peninsula, Alaska
#Monroe, Arkansas
#Morgan, Utah (cement plant?)
#Cook Illinois has second highest population
```

```{r, include = FALSE, warnings = FALSE, message = FALSE}
ec_alabama <- ec |>
 filter(str_detect(county_name, "Alabama")) |> 
  mutate(total_pop2018 = sum(pop2018))
```


```{r, echo = FALSE, message = FALSE}
ec |> 
  ggplot(aes(x = pop2018, y = ec_county)) +
  geom_point(alpha = .5) +
  geom_smooth(method = "lm", formula = y ~ x, se = FALSE, 
              color = "darkslategray4") +
    scale_x_log10(breaks = c(1000, 10000, 1000000),
                  labels = c("1,000", "10,000", "1,000,0000")) +
  labs(x = "Population of County (2018)", y = "Economic Connectedness", 
       title = "Correlation Between Population and County",
       subtitle = "There is no correlation between economic connectedness and population.") +
  theme_classic()

```

```{r, echo = FALSE, message = FALSE}
 ec |> 
  drop_na() |>
  mutate(state = str_remove(county_name, ".*, ")) |>
  group_by(state) |>
  summarise(pop_state = sum(pop2018), 
            avg_ec = mean(ec_county)) |>
  ggplot(aes(x = log(pop_state), y = avg_ec)) + 
  geom_point() + 
  geom_smooth(method = lm, se = FALSE, color = "orchid4") + 
  labs(title = "Relationship Between State Population and Average Economic Connectedness", 
       subtitle = "Bigger states have counties with lower average economic connectedness.", 
       x = "State Population (2018)", y = "Average Economic Connectedness")  +
  theme_classic()
